---
title: "lab10"
author: "celiaflorea"
date: "1/28/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Problems

1. Your task is to obtain the data from the following paper and conduct a reproducible analysis of their results.

Rosenbaum, D., Mama, Y., & Algom, D. (2017). Stand by Your Stroop: Standing Up Enhances Selective Attention and Cognitive Control. Psychological science, 28(12), 1864-1867.

Note, the paper, the data, and an existing reproducible analysis of this data is available at https://crumplab.github.io/statisticsLab/lab-10-factorial-anova.html#important-stuff-4

The re-analysis should focus only on Experiment 3. There are three main goals

  1. Reproduce as much of the analysis as possible using only paired-sample t-tests. Note,        the authors reported a 2x2 repeated measures ANOVA, but consider how the same                questions could be answered by t-tests (2 points)
  2. Reproduce a graph of the means, like shown in the paper (2 points)
  3. Present a power-curve analysis for the design. (2 points)

#note: I have had a recurring problem with the read.csv call so googled and found an alt that seems to work using readr and the read_csv call below

```{r}

library(papaja)
library(dplyr)
library(ggplot2)
library(csvread)



library(readr)
all_data <- read_csv("stroop_stand.csv")

(stand_stroop <- t.test(all_data$incongruent_stand,
                        all_data$congruent_stand, 
                        paired = TRUE))

(sit_stroop <- t.test(all_data$incongruent_sit,
                      all_data$congruent_sit,
                      paired = TRUE))
```
Reproducible analysis: 

The stroop effects in both the sitting condition `r papaja::apa_print(sit_stroop)$full_result`, and the standing condition, `r papaja::apa_print(stand_stroop)$full_result`, were highly reliable..

The authors used a repeated measures ANOVA to show that the stroop effect was smaller in the stand condition vs the sit condition. Here we used a paired sample t-test to measure the difference between the sit and stand conditions, and then apply a one-sample t-test to measure the interaction results between the two conditions and found the same result:  

```{r}

stand_stroop_scores <- all_data$incongruent_stand-all_data$congruent_stand

sit_stroop_scores <- all_data$incongruent_sit-all_data$congruent_sit

(paired_results <- t.test(stand_stroop_scores,
                          sit_stroop_scores,
                          paired = TRUE))

stroop_difference <- sit_stroop_scores - stand_stroop_scores

(interaction_results <- t.test(stroop_difference))

```
The authors note that "the most significant finding again was the shrinkage of the effect when participants were standing, F(1, 49) = 8.964, p = .004, ηp2 = .155". Using a one sample t-test we found the same result: `r apa_print(interaction_results)$full_result`.

```{r}

library(tidyr)

stroop_df <- all_data %>%
  pivot_longer(cols = 1:4,
               names_to = c("Congruency", "Posture"),
               names_sep = "_",
               values_to = "RTs")


overall_means <- stroop_df %>%
                  group_by(Posture, Congruency) %>%
                  summarise(meanRT = mean(RTs), 
                  SEMRT = (sd(RTs)/sqrt(length(RTs))))


ggplot(overall_means, aes(x = Posture, 
                          y = meanRT, 
                          group=Congruency,
                          fill=Congruency))+
    geom_bar(stat = "identity", position = "dodge")+
    theme_classic(base_size = 12)+
    ylab("Mean Reaction Time (ms)")+
    
  geom_errorbar(aes(ymin=meanRT - SEMRT, ymax=meanRT + SEMRT),
                  position= position_dodge(width = 0.9),
                  width = .2, 
                  color="blue")+
                  
    coord_cartesian(ylim = c(500, 1000))
                  
```
```{r}

effect_sizes <- seq(0, 1.5, .1)
prop_significant <- c()

for (i in 1:length(effect_sizes)) {
  sim_ps <- replicate(1000, t.test(replicate(50, rnorm(1, effect_sizes[i], 1)),
                                   mu = 0)$p.value)
  
  prop_significant[i] <- length(sim_ps[sim_ps < .05])/1000
}

plot_df <- data.frame(effect_sizes, prop_significant)

ggplot(plot_df, aes(x=effect_sizes, y=prop_significant))+
  geom_line()+
  geom_point()+
  scale_x_continuous(breaks = seq(0, 1.5, .1))+
  scale_y_continuous(breaks = seq(0, 1, .1))+
  ylab("Proportion Significant")

```




