---
title: "lab12"
author: "celiaflorea"
date: "1/31/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Problems

    Should you do a linear regression on this data? Explain.

Y <- c(10,9,8,7,6,5,4,3,2,1,2,3,4,5,6,7,8,9,10)
X <- c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19)

No, the data do not fit a linear regression. At first glance of the plot this seems to be the case- the result appears to be curvilinear and the values of X (the IV) do not permit predictions of Y (the DV). To be sure I ran the data through several of the processes from the lab12 text below and played around a bit to confirm that there is no linear correlation. Most importantly the correlation value from the cor.test = 0, shows that the relation between the variables X and Y is not linear. The p value of 1 also suggests that there is no statistically meaningful linear relation between the variables (that is, for this particular test/in the linear model).

```{r}

Y <- c(10,9,8,7,6,5,4,3,2,1,2,3,4,5,6,7,8,9,10)
X <- c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19)

plot(X,Y)

```


```{r}

some_data <- data.frame(Y_dv = Y, X_iv= X)

lm(Y_dv ~ X_iv, data = some_data)

save_model <- lm(Y_dv ~ X_iv, data=some_data)
summary(save_model)

lm(formula = Y_dv ~ X_iv, data = some_data)

cor.test(some_data$Y_dv,some_data$X_iv)

summary(save_model)$r.squared

sqrt(summary(save_model)$r.squared)

```

```{r}
library(ggplot2)

ggplot(some_data, aes(x=X_iv, y=Y_dv))+
  geom_point()+
  geom_smooth(method='lm', se=FALSE)

```

```{r}

some_data2 <- data.frame(Y = rnorm(4*10,0,1),
                         X = rnorm(4*10,0,1),
                        set = rep(1:4,each=10))

ggplot(some_data2, aes(x=X, y=Y))+
  geom_point()+
  geom_smooth(method='lm', se=FALSE)+
  facet_wrap(~set)


library(ggpmisc)
formula <- y ~ x
ggplot(some_data, aes(x= X_iv, y = Y_dv)) +
  geom_point() +
  stat_smooth(method = "lm", formula = formula) +
  stat_poly_eq(formula = formula, parse = TRUE)

```
```{r}

Y <- c(10,9,8,7,6,5,4,3,2,1,2,3,4,5,6,7,8,9,10)
X <- c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19)

sort(Y, decreasing = TRUE)
sort(X, decreasing = TRUE)

plot(X,Y)
```

