---
title: "lab5"
author: "celiaflorea"
date: "11/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Problems

#1 Trust but verify. We trust that the rnorm() will generate random deviates in accordance with the definition of the normal distribution. For example, we learned in this lab, that a normal distribution with mean = 0, and sd =1 , should only produce values larger than 2.5 with a specific small probability, that is P(x>2.5) = 0.006209665. Verify this is approximately the case by randomly sampling 1 million numbers from this distribution, and calculate what proportion of numbers are larger than 2.5. (1 point)

```{r}
pnorm(2.5, 0, 1, lower.tail = FALSE)

my_sample <- rnorm(1000000, 0, 1)

selection <- my_sample[my_sample> 2.5]

length(selection)/1000000

```

#2 If performance on a standardized test was known to follow a normal distribution with mean 100 and standard deviation 10, and 10,000 people took the test, how many people would be expected to achieve a score higher than 3 standard deviations from the mean? (1 point)

```{r}
pnorm(q=130, mean = 100, sd = 10, lower.tail = FALSE)
10000*pnorm(q=130, mean = 100, sd = 10, lower.tail = FALSE)

some_observations <- rnorm(10000, 100, 10)
length(some_observations[some_observations > 130])/10000
```

Another way to get % of values in upper tail 3 standard deviations from mean? (99.73% of values should be below 3rd deviation) 

```{r}
pnorm(q=130, mean = 100, sd = 10, lower.tail = FALSE)/.9973

```

#3 You randomly sample 25 numbers from a normal distribution with mean = 10 and standard deviation = 20. You obtain a sample mean of 12. You want to know the probability that you could have received a sample mean of 12 or larger. Create a sampling distribution of the mean for this scenario with at least 10,000 sample means (1 point). Then, calculate the proportion of sample means that are 12 or larger (1 point).

```{r}

sampling_distribution <- replicate(10000, mean(rnorm(25, 10, 20)))
hist(sampling_distribution)

length(sampling_distribution[sampling_distribution >=12])/10000

```


#4 You randomly sample 100 numbers from a normal distribution with mean = 10 and standard deviation = 20. You obtain a sample mean of 12. You want to know the probability that you could have received a sample mean of 12 or larger. Create a sampling distribution of the mean for this scenario with at least 10,000 sample means. Then, calculate the proportion of sample means that are 12 or larger. Is the proportion different from question 3, why? (1 point).

```{r}

sampling_distribution <- replicate(10000, mean(rnorm(100, 10, 20)))
hist(sampling_distribution)

length(sampling_distribution[sampling_distribution >=12])/10000

```
#4 continued: Yes the proportion of samples with means of 12 or greater is larger in question 3 than (roughly double that) in question 4. This is because of the central limit theorum- the larger the sample, the more closely the sample means will reflect the population mean. In this instance in problem number 3 the sample size of n=25 with a mean of 10 and standard deviation of 20 produces samples with a mean equal to or larger than 12 around 1/3  of the time. In question 4 we have a larger sample of n=100 (same mean and SD) and find sample means of 12 or greater roughly around 1/6 of the time because of the larger samples sizes (100 vs 25) in question 4 the sample means will be closer to the true population mean. 




#5 You randomly sample 25 numbers from a normal distribution with mean = 10 and standard deviation = 20. You obtain a sample standard deviation of 15. You want to know the probability that you could have received a sample standard deviation of 15 or less. Create a sampling distribution of standard deviations for this scenario with at least 10,000 sample standard deviations. Then, calculate the proportion of sample standard deviations that are 15 or less. (1 point)

```{r}

sampling_distribution <- replicate(10000, sd(rnorm(25, 10, 20)))
hist(sampling_distribution)

length(sampling_distribution[sampling_distribution <= 15])/10000

```

