---
title: "lab8"
author: "celiaflorea"
date: "1/24/2021"
output: html_document
---

1. Write a function to convert a vector of raw-scores into z-scores. The function should have inputs for the vector, the mean and sd of the normal distribution, and should return a vector of zscores. (1 point). Also, demonstrate that the function works correctly (1 point). How you make the demonstration is up to you.

- Advanced: Have an option so that the function will convert the raw scores to zscores in one of two ways:
  - using user provided mean and standard deviation
  - using the calculated mean and standard deviation from the raw scores
  
```{r}

to_zscores <- function(raw, mu, sd){
  zscores <- (raw-mu)/sd
  return(zscores)
} 

some_numbers <- c(1,2,3,4,5)

to_zscores(some_numbers, 5, 1)

to_zscores_b <- function (raw, mu = NULL, sdev = NULL){
  if (is.null(mu) == TRUE) mu <- mean(raw) 
  if (is.null (sdev) == TRUE) sdev <- sd(raw) 
  zscores <- (raw-mu)/sdev
  return(zscores)
}

to_zscores_b(some_numbers)

```

2. Base R does not have a function for a z-test. Write a function to accomplish a one-sample z-test. Remember, a one-sample z test is used to compare the probability of obtaining the sample mean (or larger or smaller) if it came from a known normal distribution. (2 points).

- Use your z-test function to conduct a test of the following. A sample of 25 scores is taken. The mean of the sample is 50. The sample is assumed to have been taken from a normal distribution with mean 40 and standard deviation 7. Report a one-tailed z-test, examining the probability of obtaining a sample of greater than 50 in this situation. Report the results, and give a brief sentence explaining the result and the inference you make (2 points).

```{r}

z.test <- function(sample_mean, sample_size, mu, sigma) {
  sampling_dist_mean <- mu
  sampling_dist_sd <- sigma/sqrt(sample_size)
  
 p_value <-  pnorm(sample_mean, sampling_dist_mean ,sampling_dist_sd, lower.tail = FALSE)
  return(p_value)
}

z.test(sample_mean = 50, 
       sample_size = 25,
       mu = 40,
       sigma = 7)


z.test(1,1,0,1)


```
The probability of finding a sample mean greater than 50 within the specified population parameters is very small (z=4.570531e-13, area beyond z=0). This makes sense since with a population mean of 40 and sigma/standard deviation of 7, the sample mean of 50 is already more than one whole standard deviation from the population mean. (The substantial difference between population and sample means is likely due to the smallish sample size of n=25.)
```{r}

z.test <- function(sample_mean, sample_size, mu, sigma, two.tailed=TRUE) {
  sampling_dist_mean <- mu
  sampling_dist_sd <- sigma/sqrt(sample_size)
  
 p_value <- pnorm(sample_mean, sampling_dist_mean, sampling_dist_sd, lower.tail = FALSE)
  return(p_value)


if(two.tailed == TRUE) p_value <- p_value*2
}

z.test(sample_mean = 37, 
       sample_size = 5,
       mu = 40,
       sigma = 7,
       two.tailed = FALSE)

##



z.test <- function(sample_mean, 
                   sample_size, 
                   mu, 
                   sigma, 
                   two.tailed=TRUE) {
  
    
    sampling_dist_mean <- mu
    sampling_dist_sd <- sigma/sqrt(sample_size)
    
    abs_difference <- abs(sample_mean - mu)
    
   p_value <- pnorm((mu+abs_difference),sampling_dist_mean,sampling_dist_sd,lower.tail = FALSE)
  
  
  if(two.tailed == TRUE) p_value <- p_value*2
   return(p_value)
   

}


z.test(sample_mean = 37, 
       sample_size = 5,
       mu = 40,
       sigma = 7,
       two.tailed = FALSE)




```

