---
title: "lab9"
author: "celiaflorea"
date: "1/24/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. The following paper links to open data, and describes a design where two chi-square tests are performed for Experiment 1 (A copy of this paper will be made available).

Silver, A. M., Stahl, A. E., Loiotile, R., Smith-Flores, A. S., & Feigenson, L. (2020). When Not Choosing Leads to Not Liking: Choice-Induced Preference in Infancy. Psychological Science, 0956797620954491.

Obtain the data from the online repository, show your code for loading it into R, then conduct the same tests reported in Experiment 1 that the authors conducted. These include one binomial test, and two chi-square tests. Briefly report your re-analysis, and discuss whether you obtained the same values as the authors did (6 points).





```{r}

library(xlsx)
library(csvread)

the_data <- read.csv("lab9/When not choosing leads to not liking_Data.csv")

```



```{r}
library(dplyr)

e1_data <- the_data %>%
  filter(ExperimentNumber == "1")

sum_C <- sum(e1_data$Infant.Chose.C)
total_C <- length(e1_data$Infant.Chose.C)

(binomial_p <- pbinom(q = total_C - sum_C, size = total_C, prob = .5, lower.tail = TRUE)*2)

```

```{r}

library(tidyr)

gender_choice_table <- e1_data %>%
  group_by(Gender, Infant.Chose.C) %>%
  summarize(counts = n()) %>%
  pivot_wider(names_from = c(Gender),
              values_from = counts)

gender_choice_table <- gender_choice_table[2:3]

(gender_Xsq <- chisq.test(gender_choice_table))

uncorrected_Xsq <- sum((gender_Xsq$observed-gender_Xsq$expected)^2/gender_Xsq$expected)

gender_Xsq_unc <- pchisq(uncorrected_Xsq,1,lower.tail = FALSE)


```


```{r}

age_table <- e1_data %>%
    group_by (AgeMonths, Infant.Chose.C) %>%
    summarize(counts = n()) %>%
    pivot_wider(names_from = c(AgeMonths), values_from = counts)

age_table[is.na(age_table)] <- 0

age_table <- as.matrix(age_table[2:21])

    (age_xs <- chisq.test(age_table))


age_xs$observed
age_xs$expected

```
Reproducible report: 


However, in the critical test trial that followed, `r sum_C` of `r total_C` infants (`r round(sum_C/total_C, digits = 2)`%),  chose the new block (block C; Fig. 1)—a percentage significantly different from chance, according to a two-tailed binomial test, p = `r round(binomial_p,digits=3)`, 95% exact confidence interval (CI) = [52.83%, 91.78%], relative risk ratio = 1.52. A chi-square test of independence indicated no significant effect of age or gender on infants’ choices, $\chi^2$ (`r age_xs$parameter`), N=  `r round(sum(age_xs$observed), digits=2)` = `r round(age_xs$statistic, digits = 2)`, p=`r round(age_xs$p.value, digits = 3)`,and $\chi^2$ (1,N=21)=`r round(uncorrected_Xsq, digits = 2)`,p= `r round(gender_Xsq_unc,digits=3)`, respectively.

Discussion:

So I have reproduced the report, consistent with the original. However, as noted in lab the authors seem to have mistreated the data in the age category. Looking at the ages, and considering the small sample, it does not appear the range of ages would allow us to bin these into groups that would be evenly distributed. Ultimately, a larger sample is probably required to compare between the age groups to see if there is a meaningful difference in their choices/behavior depending upon age. 