---
title: "lab9"
author: "celiaflorea"
date: "1/24/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. The following paper links to open data, and describes a design where two chi-square tests are performed for Experiment 1 (A copy of this paper will be made available).

Silver, A. M., Stahl, A. E., Loiotile, R., Smith-Flores, A. S., & Feigenson, L. (2020). When Not Choosing Leads to Not Liking: Choice-Induced Preference in Infancy. Psychological Science, 0956797620954491.

Obtain the data from the online repository, show your code for loading it into R, then conduct the same tests reported in Experiment 1 that the authors conducted. These include one binomial test, and two chi-square tests. Briefly report your re-analysis, and discuss whether you obtained the same values as the authors did (6 points).


```{r}

library(xlsx)

the_data <- xlsx::read.xlsx("lab9/When not choosing leads to not liking_Data.xlsx", sheetIndex = 1)

the_data <- read.csv(file="lab9/infant_choice_data.csv")

library(dplyr)
e1_data <- the_data %>%
  filter(ExperimentNumber == "1")
```
```{r}

the_data <- xlsx::read.xlsx(When_not_choosing_leads_to_not_liking_Data.xlsx, sheetIndex = 1)

the_data <- read.csv(file="infant_choice_data.csv")


```

